---
title: "Opinary Data"
output: 
  html_document:
    code_folding: hide
---

## Explanations

Data provided from [Opinary](https://opinary.com/de/home-de/)

Data selection:

- January 2018 - Mai 2019
- Polls are limited to those with >5,000 responses (votes)
- Polls are limited to those that appeared on >2 publisher sites
- Qualitative (read: human) assessment as to whether they would be polls which could help to determine political orientation

Vote position:

- Measured on a range between 0 and 1:
  - 0 = leftmost position 
  - 1 = rightmost position

- Segmented into thirds:
  - <.33 = "left"; 
  - .34-.66 = "middle" 
  - .67+ = "right"


```{r message=FALSE, warning=FALSE}
# import libraries
library(readxl)
library(tidyverse)
library(patchwork)

# global options
knitr::opts_chunk$set(fig.width=10, fig.height=8, fig.align = "center") 

# import data
opinary <- read_excel("../data/Publisher political orientation polls.xlsx", sheet = "Data") %>%
  mutate(label = ifelse(vote_position=="left",leftlabel,rightlabel),
         label = ifelse(vote_position=="middle","",label),
         label_order = ifelse(vote_position=="left",1,2),
         label_order = ifelse(vote_position=="right",3,label_order)
         ) %>%
  #select(-leftlabel, -rightlabel) %>%
  group_by(poll_id) %>%
  # get number of total votes/poll
  mutate(vote_sum = sum(votes)) %>%
  ungroup() %>%
  # keep polls with > 1000 votes
  filter(vote_sum > 1000) %>%
  mutate(vote_share = votes/vote_sum)
```

```{r}
opinary %>%
  mutate(vote_share = round(vote_share,2)) %>%
  select(poll_customer_id, header, label, vote_position, votes, vote_sum, vote_share) %>%
  sample_n(10) %>% htmlTable::htmlTable(align="l")
```

## Number of total votes

```{r fig.height=6, fig.width=5, fig.align="center"}
p <- opinary %>% 
  group_by(poll_customer_id) %>%
  summarise(vote_sum = sum(votes)) %>%
  ggplot(aes(reorder(poll_customer_id, vote_sum), vote_sum, text = vote_sum)) +
  geom_col(fill="darkred", alpha=0.7) +
  coord_flip() +
  ggthemes::theme_hc() +
  labs(x=NULL, y="Total votes") +
  ylim(0, 3800000)

plotly::ggplotly(p, tooltip = c("text"))
```

## Topics

```{r}
check_polls <- function(df, topics) {
  
  df %>% 
    # Add filter
    filter(grepl(topics, header, ignore.case = T)) %>%
    group_by(header, label) %>%
    tally() %>%
    select(-n) %>%
    htmlTable::htmlTable(align="l", rnames=F)
}
```

```{r}
plot_polls <- function(df, topics, pos_labels, neg_labels) {
  
  topic_df <- df %>%
    # Add filter
    filter(grepl(topics, header, ignore.case = T)) %>%
    group_by(poll_customer_id, header, label) %>%
    summarise(
      votes = sum(votes),
      vote_share = mean(vote_share)
      ) %>%
    ungroup() %>%
    group_by(poll_customer_id) %>%
    mutate(vote_sum = sum(votes)) %>% 
    ungroup() %>%
    # create labels
    mutate(
      short_label = ifelse(grepl(pos_labels, label, ignore.case = T),"+",""),
      short_label = ifelse(grepl(neg_labels, label, ignore.case = T),"-",short_label),
      long_label = paste(label,"(",votes,")")
      ) %>%
    group_by(poll_customer_id, header, short_label) %>%
    summarise(
      vote_share = mean(vote_share),
      vote_mean = sum(votes),
      labels = paste(long_label, collapse = "\n")
      ) %>% ungroup() %>%
    mutate(
      label_order = ifelse(short_label =="+",0,1),
      label_order = ifelse(short_label =="" ,1,label_order),
      label_order = ifelse(short_label =="-",2,label_order)
      )
  
  p <- topic_df %>%
    ggplot(aes(reorder(short_label,label_order), 
               poll_customer_id, fill=vote_share, text = labels
               )) +
    geom_tile() +
    geom_text(aes(label= round(vote_share,2)), size=3) +
    ggthemes::theme_hc() +
    facet_wrap(.~header, ncol = 2, scales = "free") +
    scale_fill_gradient2(low = "#6993c9", mid="#fcf8f7", high="#8b312e") +
    labs(x=NULL, y=NULL, title="Proportion of votes (# of votes)") +
    theme(axis.text.x = element_text(size = 6),
          legend.position='none')
  
  plotly::ggplotly(p, tooltip = c("text"))
  
}
```

### 1. National

#### AfD
```{r}
key = "afd"

check_polls(opinary, key)
```

```{r}
pos <- paste("Ja","Gut", sep="|")
neg <- paste("Nein", "Schlecht", sep="|")

plot_polls(opinary, key, pos, neg)
```

#### Islam, Rechtsextremismus, Antisemitismus
```{r}
keys = paste("islam","rechtsextrem", "antisemitismus", sep ="|")

check_polls(opinary, keys)
```

```{r fig.height=6}
pos <- "Ja" 
neg <- "Nein"

plot_polls(opinary, keys, pos, neg)
```

#### CDU, Koalition
```{r}
keys = paste("merkel","koalition", sep ="|")

check_polls(opinary, keys)
```

```{r fig.height=6}
pos <- "Ja" 
neg <- "Nein"

plot_polls(opinary, keys, pos, neg)
```

#### Cannabis, Alkohol
```{r}
keys = paste("cannabis","alkohol", sep ="|")

check_polls(opinary, keys)
```

```{r fig.height=4}
pos <- "Ja" 
neg <- "Nein"

plot_polls(opinary, keys, pos, neg)
```

#### Diesel-Fahrverbote, E-Mobilit채t, Klimawandel, ...
```{r}
keys <- paste("diesel","e-mobilit채t", "klimawandel", "cannabis", sep ="|")

check_polls(opinary, keys)
```

```{r}
pos <- paste("Ja","Gut", sep="|")
neg <- paste("Nein", "Dagegen", sep="|")

plot_polls(opinary, keys, pos, neg)
```

#### Gehalt, Warnstreiks
```{r}
keys = paste("gehalt", "warnstreiks", sep ="|")

check_polls(opinary, keys)
```

```{r fig.height=4}
pos <- "Ja" 
neg <- "Nein"

plot_polls(opinary, keys, pos, neg)
```

### 2. International

#### Trump
```{r}
key <- "trump"

check_polls(opinary, key)
```

```{r}
pos <- paste("Ja","Viel", sep="|")
neg <- paste("Nein", "Gar nichts", sep="|")

plot_polls(opinary, key, pos, neg)
```

#### Brexit
```{r}
key <- "brexit"

check_polls(opinary, key)
```

```{r fig.height=6}
pos <- "Ja"
neg <- "Nein"

plot_polls(opinary, key, pos, neg)
```

#### Nato, T체rkei, Syrien
```{r}
keys <- paste("nato","t체rkei", "tuerkei", "syrien", sep ="|")

check_polls(opinary, keys)
```

```{r}
pos <- "Ja"
neg <- "Nein"

plot_polls(opinary, keys, pos, neg)
```

#### EU
```{r}
keys <- paste("notre","asyl", sep ="|")

check_polls(opinary, keys)
```

```{r fig.height=4}
pos <- "Ja"
neg <- "Nein"

plot_polls(opinary, keys, pos, neg)
```
