---
title: "Political orientation and consumption of online news"
author: "Franziska Löw"
date: "20.01.2019"
output: html_document
---

Since 2012, the [Reuters Institute Digital News Survey](http://www.digitalnewsreport.org/about-us-2018/) has been investigating the media use of digital content. Among others, the following questions are investigated: What websites do you visit to access news online? What is your political orientation?

The study is being conducted simultaneously in 37 countries under the coordination of the Reuters Institute for the Study of Journalism, based in Oxford (UK). [The Hans Bredow Institute](https://www.hans-bredow-institut.de/de/projekte/reuters-institute-digital-news-survey) has been responsible for the German part of the study as a cooperation partner since 2013. Fieldwork was undertaken between 19th - 22nd January 2018 conducting an online survey. Total sample size for Germany was 2038 adults (aged 18+) who access news once a month or more. 

**Net sample Germany**:

  - n = 2038
  - male 49 % / female 51 %
  - 18 - 24: 9 %
  - 25 - 34: 15 %
  - 35 - 44: 15 %
  - 45 - 54: 20 %
  - 55+: 41 %

 
```{r include=FALSE}
library(tidyverse)
library(ggthemes)
library(patchwork)
rm(list=ls())

reutersDF1 <- readxl::read_excel("../data/reuters_clean.xlsx")
reutersDF2 <- readxl::read_excel("../data/reuters_clean.xlsx", sheet = "orientation")
```

## Isolated results

### News websites

Q5b. Which of the following brands have you used to access news online in the last week (via websites, apps, social media, and other forms of Internet access)? Please select all that apply.

```{r include=FALSE}
keeps <- c("Bild.de", "Spiegel Online","Welt Online","Focus Online", "Stern.de","ZEIT Online","Tagesschau.de")
```

```{r echo=FALSE, fig.align="centre", fig.height=6}
reutersDF1 %>%
  gather(key = "orientation", value = "count", -medium) %>%
  group_by(medium) %>%
  summarise(count = sum(count)) %>%
  mutate(insample = ifelse(medium %in% keeps, TRUE, FALSE)) -> reutersDF1.grouped

p <- reutersDF1.grouped %>%
  ggplot(aes(reorder(medium,count),count
             #fill = insample
             )) +
  geom_col(fill = "#00AFBB", alpha = 0.9) +
  coord_flip() +
  labs(x = NULL, y = NULL, 
       title = "Which of the brands have you used to access news online in the last week?",
       subtitle = paste("n=", sum(reutersDF1.grouped$count)),
       caption = "Reuters Institute Digital News Report 2018")

plotly::ggplotly(p, tooltip="y")
```

### Political orientation

Q1F. Some people talk about 'left', 'right' and 'centre' to describe parties and politicians. (Generally socialist parties would be considered ‘left wing’ whilst conservative parties would be considered ‘right wing’). With this in mind, where would you place yourself on the following scale?

```{r echo=FALSE}
p<- reutersDF2 %>%
  mutate(count_rel = 100*(count/2038),
    partisan_scale = ifelse(partisan == "Very left-wing", -3,NA),
         partisan_scale = ifelse(partisan == "Fairly left-wing", -2, partisan_scale),
         partisan_scale = ifelse(partisan == "Slightly left-of-centre", -1,partisan_scale),
         partisan_scale = ifelse(partisan == "Centre", 0, partisan_scale),
         partisan_scale = ifelse(partisan == "Slightly right-of-centre", 1, partisan_scale),
         partisan_scale = ifelse(partisan == "Fairly right-wing",2, partisan_scale),
         partisan_scale = ifelse(partisan == "Very right-wing", 3, partisan_scale)
  ) %>%
  ggplot(aes(reorder(partisan, partisan_scale), count 
            # label = paste(round(count_rel, digits = 1),"%")
            )) +
  geom_col(fill = "#00AFBB", alpha = 0.9) +
  #geom_text(vjust = 1) +
  labs(title = "Where would you place yourself on the following scale?",
       subtitle = "n= 2038",
       caption = "Results for Germany / Hans-Bredow-Institut"
       ) +
  theme(axis.title = element_blank(),
        axis.text.y = element_blank(),
        axis.text.x = element_text(angle = 90),
        axis.ticks.y = element_blank())

plotly::ggplotly(p, tooltip="y")
```

## Combined results

### 7-point Scale

```{r include=FALSE}
reutersDF.long <- reutersDF1 %>%
  select(medium:`Very rightwing`) %>%
  mutate(order = Centre) %>%

  gather(partisan, count, `Very leftwing`:`Very rightwing`) %>%
  mutate(partisan.f = as.factor(partisan)) %>%
  mutate(
    partisan_scale = ifelse(partisan == "Very leftwing", -3,NA),
         partisan_scale = ifelse(partisan == "Fairly leftwing", -2, partisan_scale),
         partisan_scale = ifelse(partisan == "Slightly leftofcentre", -1,partisan_scale),
         partisan_scale = ifelse(partisan == "Centre", 0, partisan_scale),
         partisan_scale = ifelse(partisan == "Slightly rightofcentre", 1, partisan_scale),
         partisan_scale = ifelse(partisan == "Fairly rightwing",2, partisan_scale),
         partisan_scale = ifelse(partisan == "Very rightwing", 3, partisan_scale)
  ) 
```

```{r include=FALSE}
reutersDF.long <- reutersDF.long %>%
  
  # group by partisan 
  group_by(partisan.f) %>%
  mutate(count_sum_p = sum(count)) %>%
  ungroup() %>%
  
  # group by medium
  group_by(medium) %>%
  mutate(count_sum_m = sum(count)) %>%
  ungroup() %>%
  
  # calulate relative counts by partisan and medium
  mutate(count_relative_p = count/count_sum_p,
         count_relative_m = count/count_sum_m,
         order_relative_p = order/count_sum_p,
         order_relative_m = order/count_sum_m
         )
  
```

#### Absolute values

```{r echo=FALSE, fig.height=8, fig.width=8, fig.align="center"}
p<- reutersDF.long %>%
  filter(!grepl("know",medium)) %>%
  filter(!grepl("None",medium)) %>%
  #filter(medium %in% keeps) %>%
  ggplot(aes(reorder(partisan.f, partisan_scale),reorder(medium, order), fill = count)) +
  geom_tile() +
  geom_text(aes(label= count), size = 3) +
  scale_fill_gradient(low =  "#00AFBB", high = "#FC4E07") +
  theme_calc() +
  labs(title = "Reuters Institute Digital News Report 2018",
       subtitle = "Political orientation and media consumption",
       caption = "Results for Germany / Hans-Bredow-Institut",
       x = NULL, y = NULL)+ 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(legend.position = "none",
       axis.text.x = element_text(angle = 90))

p
```

#### Relative values

```{r echo=FALSE, fig.height=8, fig.width=10, fig.align="centre"}
p1 <- reutersDF.long %>%
  filter(!grepl("know",medium)) %>%
  filter(!grepl("None",medium)) %>%
  #filter(medium %in% keeps) %>%
  ggplot(aes(reorder(partisan.f, partisan_scale),
             reorder(medium, order_relative_m), 
             fill = count_relative_m)) +
  geom_tile() +
  geom_text(aes(label=round((count_relative_m*100), digits = 1) ), size = 3) +
  scale_fill_gradient(low =  "#00AFBB", high = "#FC4E07") +
  theme_calc() +
  labs(title = "Reuters Institute Digital News Report 2018",
       subtitle = "Absolute values / row sum",
       x = NULL, y = NULL) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(legend.position = "none",
       axis.text.x = element_text(angle = 90))

p2 <- reutersDF.long %>%
  filter(!grepl("know",medium)) %>%
  #filter(medium %in% keeps) %>%
  group_by(medium) %>%
  summarise(count_sum = sum(count),
            order_relative_m = sum(order_relative_m)) %>%
  ggplot(aes(reorder(medium,order_relative_m), count_sum)) +
  geom_col(fill = "#00AFBB", alpha = 0.8) +
  geom_text(aes(label=count_sum), hjust = 1, size = 3) +
  coord_flip() +
  theme_calc() +
  labs(y = NULL, x = NULL,
       caption = "Results for Germany / Hans-Bredow-Institut") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
        )

p1 + p2 + plot_layout(widths = c(2,1))

#ggsave("../figs/reuters.png", width = 12, height = 10)
```

```{r eval=FALSE, fig.align="centre", fig.height=6, fig.width=8, include=FALSE}
p1 <- reutersDF.long %>%
  filter(medium %in% keeps) %>%
  ggplot(aes(reorder(partisan.f, partisan_scale),
             reorder(medium, order_relative_m), 
             fill = count_relative_m)) +
  geom_tile() +
  geom_text(aes(label=round((count_relative_m*100), digits = 1) ), size = 3) +
  scale_fill_gradient(low =  "#00AFBB", high = "#FC4E07") +
  theme_calc() +
  labs(title = "Reuters Institute Digital News Report 2018",
       subtitle = "Political orientation and media consumption",
       x = NULL, y = NULL) + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(legend.position = "none",
       axis.text.x = element_text(angle = 90))

p2 <- reutersDF.long %>%
  filter(medium %in% keeps) %>%
  group_by(medium) %>%
  summarise(count_sum = sum(count),
            order_relative_m = sum(order_relative_m)) %>%
  ggplot(aes(reorder(medium,order_relative_m), count_sum)) +
  geom_col(fill = "#00AFBB", alpha = 0.8) +
  geom_text(aes(label=count_sum), hjust = 1, size = 3) +
  coord_flip() +
  theme_calc() +
  labs(y = NULL, x = NULL,
       caption = "Results for Germany / Hans-Bredow-Institut") +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
        )

p1 + p2 + plot_layout(widths = c(2,1))
```

```{r eval=FALSE,fig.align="centre", fig.height=10, fig.width=8, include=FALSE}
p1 <- reutersDF.long %>%
  filter(!grepl("know",medium)) %>%
  filter(!grepl("None",medium)) %>%
  ggplot(aes(reorder(partisan.f, partisan_scale),medium, fill = count_relative_p)) +
  geom_tile() +
  geom_text(aes(label=round((count_relative_p*100), digits = 1) ), size = 3) +
  scale_fill_gradient(low =  "#00AFBB", high = "#FC4E07") +
  theme_calc() +
  labs(x = "", y = "") + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(legend.position = "none",
       axis.text.x = element_text(angle = 90))

p2 <- reutersDF.long %>%
    filter(!grepl("know",medium)) %>%
  #filter(medium %in% keeps) %>%
  group_by(partisan.f, partisan_scale) %>%
  summarise(count_sum = sum(count)) %>%
  ggplot(aes(reorder(partisan.f, partisan_scale), count_sum)) +
  geom_col(fill = "#00AFBB", alpha = 0.8) +
  geom_text(aes(label=count_sum), vjust = 1, size = 3) +
  theme_calc() +
  labs(y = NULL, x = NULL, title = "Relative values II",
       subtitle = "Absolute values/sum by political orientation") +
  theme(axis.text.x = element_blank(),
        axis.ticks.x = element_blank()
        )

p2 + p1 + plot_layout(ncol = 1, heights = c(1,2))
```

### 3-point scale
```{r include=FALSE}
reutersDF.long <- reutersDF1 %>%
  select(medium, `Left`:`Right`) %>%
  mutate(order = Centre__1) %>%

  gather(partisan, count, `Left`:`Right`) %>%
  mutate(partisan.f = as.factor(partisan)) %>%
  mutate(
         partisan_scale = ifelse(partisan == "Left", -1, 0),
         partisan_scale = ifelse(partisan == "Centre__1",0, partisan_scale),
         partisan_scale = ifelse(partisan == "Right", 1, partisan_scale)
  )
```

```{r include=FALSE}
reutersDF.long <- reutersDF.long %>%
  
  # group by partisan 
  group_by(partisan.f) %>%
  mutate(count_sum_p = sum(count)) %>%
  ungroup() %>%
  
  # group by medium
  group_by(medium) %>%
  mutate(count_sum_m = sum(count)) %>%
  ungroup() %>%
  
  # calulate relative counts by partisan and medium
  mutate(count_relative_p = count/count_sum_p,
         count_relative_m = count/count_sum_m,
         
         order_relative_p = order/count_sum_p,
         order_relative_m = order/count_sum_m
         )
  
```

#### Absolute values

```{r echo=FALSE, fig.height=8, fig.width=8}
reutersDF.long %>%
  filter(!grepl("know",medium)) %>%
  filter(!grepl("None",medium)) %>%
  ggplot(aes(reorder(partisan.f, partisan_scale), 
             reorder(medium, order), fill = count)) +
  geom_tile() +
  geom_text(aes(label=count), size = 3) +
  scale_fill_gradient(low =  "#00AFBB", high = "#FC4E07") +
  theme_calc() +
  labs(x = "", y = "", title = "Reuters Institute Digital News Report 2018",
       subtitle = "Political orientation and media consumption",
       caption = "Results for Germany / Hans-Bredow-Institut") + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(legend.position = "none",
       axis.text.x = element_text(angle = 90))
```

#### Relative values

```{r echo=FALSE, fig.height=8, fig.width=10}
p1 <- reutersDF.long %>%
    filter(!grepl("know",medium)) %>%
  filter(!grepl("None",medium)) %>%
  ggplot(aes(reorder(partisan.f, partisan_scale),
             reorder(medium, order_relative_m), 
             fill = count_relative_m)) +
  geom_tile() +
  geom_text(aes(label=round((count_relative_m*100), digits = 1) ), size = 3) +
  scale_fill_gradient(low =  "#00AFBB", high = "#FC4E07") +
  theme_calc() +
  labs(x = "", y = "", 
       title = "Reuters Institute Digital News Report 2018",
       subtitle = "Political orientation and media consumption",
       caption = "Results for Germany / Hans-Bredow-Institut") + 
  scale_x_discrete(expand = c(0, 0)) +
  scale_y_discrete(expand = c(0, 0)) +
  theme(legend.position = "none",
       axis.text.x = element_text(angle = 90))

p2 <- reutersDF.long %>%
  filter(!grepl("know",medium)) %>%
  filter(!grepl("None",medium)) %>%
  group_by(medium) %>%
  summarise(count_sum = sum(count),
            order_relative_m = sum(order_relative_m)) %>%
  ggplot(aes(reorder(medium, order_relative_m) ,count_sum)) +
  geom_col(fill = "#00AFBB", alpha = 0.8) +
  geom_text(aes(label=count_sum), hjust = 1, size = 3) +
  coord_flip() +
  theme_calc() +
  labs(y = NULL, x = NULL) +
  theme(axis.text.y = element_blank(),
        axis.ticks.y = element_blank()
        )

p1 + p2 + plot_layout(widths = c(2,1))
```

