---
title: "Different types of media bias - visibility bias"
author: "Franziska Löw"
date: "`r format(Sys.Date())`"
output: html_document
---

```{r include=FALSE}
rm(list = ls())

library(tidyverse)
library(ggthemes)
library(lubridate)

load("../output/data_step2.Rda")
```

The visibility of a party or a candidate is important as the visibility of political actors in media coverage will increase their accessibility to audiences, influencing subsequent political judgments. Studies combining media content data with voter surveys have indeed found that voters tend to infer a party's political importance from its media salience.

To determine visibility bias, we first need to measure visibility per se. A party is treated as visible in an article if the party itself is mentioned in an article (if an article contains the word "SPD", "CDU"/"CSU/Union","FDP","Grüne","AfD" or "Linke") ( [Eberl, 2017](https://journals.sagepub.com/doi/abs/10.1177/0093650215614364) )

## Visibility

The visibility of a party $p$ in a newspaper $s$ is defined as the number of news articles published by the newspaper on that party (e.g. articles that contain the name of the party), normalised on the total amount of articles by that newspaper in the corpus.

$$
\text{visibility}(p,s) = \frac{\text{#Articles}_{p,s}}{\text{#Articles}_s}
$$

```{r claculate total amount of articles by newspaper, include=FALSE}
btw <- btw %>% 
  mutate(month = month(date),
         year = year(date)) %>%
  group_by(medium, month, year) %>%
  dplyr::mutate(articles_s = n()) %>%
  ungroup()
```

```{r count party mentions, include=FALSE}
parties <- c("SPD",paste("CDU","CSU","Union",sep = "|"),"FDP","Grüne","AfD","Linke")

rm(vis)

for (party in parties) {
  
    tempdf <- btw %>% 
      # filter all articles that contain the party as a word
      filter(grepl(party,text, ignore.case = T)) %>%
      # calculate the number of articles by each newspaper
      group_by(medium, month, year) %>%
      summarize(
        # pass the total amount of articles to the grouped df
        articles_s = mean(articles_s),
        # calculate the number of articles about a party in a newsletter
        articles_p_s = n()) %>% ungroup() %>%
      mutate(
        party = party,
        # calculate relative amount
        vis = articles_p_s/articles_s)
    
  if (exists('vis')) {
   vis <- bind_rows(vis, tempdf) 
  } else {
    vis <- tempdf
  }
}

vis <- vis %>% mutate(party = ifelse(grepl("CDU",party), "Union",party))
```

```{r echo=FALSE}
vis %>%
  group_by(medium,party) %>%
  summarize(visibility_p_s = mean(visibility_p_s, na.rm = T)) %>%
  select(medium, party, visibility_p_s) %>%
  spread(key = party, value = visibility_p_s) %>%
  ggiraphExtra::ggRadar(aes(color = medium),
                        interactive = T,
                        alpha = 0,
                        rescale = F,
                        legend.position = "right") 
```



```{r eval=FALSE, include=FALSE}
save(vis, file = "../output/visibility.Rda")
```

